---
title: "dumbmeinregression tutorial"
author: "Shuoyuan Gao"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dumbmeinregression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dumbmeinregression)
```

## Overall function

This package include two linear regression models.`slr` : Simple Linear regression model and `mlr` : multiple linear regression model. And three other functions: `Confiden_inter` : confidence interval, `plot_regression` : plot the x and y relationship and `r_squared` : calculate the R-square with or without adjusted R-square.

## dataset simulation

```{r}
set.seed(123)
X1= rnorm(100)
X2= rnorm(100)
X3= rnorm(100)
y= 5 + 2*X1 + 7*X2 + 0.1*X3 + rnorm(100, sd = 5)
simulate_data1= data.frame(y, X1, X2, X3)

#we are setting the lowercase x as only variable for simple linear regression
x = simulate_data1$X1
#uppercase X is two variables
X = cbind(simulate_data1$X1, simulate_data1$X2)
y = simulate_data1$y
```

usage of the functions in the package
```{r}
#you can use slr() get $Beta0, $Beta1, $Fitted values, $Residuals values.
slr_result = slr(x, y)

print(slr_result)
```

```{r}
#use mlr() get the mutiple linear regression model. But be careful, we are using uppercase X.
mlr_result = mlr(X, y)

print(mlr_result)
```


```{r}
#use ci() get the confidence interval. But be carefull, we are using uppercase X. And the default level is 0.05.
Confiden_inter_result = ci(X, y, alpha = 0.05)

print(Confiden_inter_result)
```


```{r}
#use this to plot_regression() plot x and y
plot_regression_result = plot_regression(x, y)

print(plot_regression_result)
```


```{r}
fitted_values = slr_result$FittedValues

#use r_squared() get R-square 
r_squared_result_without_adjustedR = r_squared(y, fitted_values, p = 1, withadjr = FALSE)
print(r_squared_result_without_adjustedR)
```

```{r}
fitted_values = slr_result$FittedValues

#use r_squared() and withadjr = TRUE get R-square with adjusted R-square.
r_squared_result_with_adjustedR = r_squared(y, fitted_values, p = 1, withadjr = TRUE)

print(r_squared_result_with_adjustedR)
```



Now we comparing against the original R functions on simulated to demonstrate the correctness
```{r}
lm_slr_model= lm(y ~ X1, data = simulate_data1)

all.equal(slr_result$Beta0, coef(lm_slr_model)[1], check.attributes = FALSE)
all.equal(slr_result$Beta1, coef(lm_slr_model)[2], check.attributes = FALSE)
```

```{r}
lm_mlr_model= lm(y ~ X, data = simulate_data1)

all.equal(as.numeric(mlr_result$Beta), coef(lm_mlr_model), check.attributes = FALSE)
```


```{r}
lm_model= lm(y ~ X)
lm_ci= confint(lm_model)

package_ci= ci(X, y)
package_ci_matrix= as.matrix(package_ci)

all.equal(package_ci_matrix, lm_ci, check.attributes = FALSE)
```

```{r}
plot(x, y)
plot_regression(x,y)
```




```{r}
lm_model1= lm(y ~ fitted_values)
r_squared_builtin = summary(lm_model1)$r.squared

r_squared_result_without_adjustedR = r_squared(y, fitted_values, p = 1, withadjr = FALSE)$R_Squared

all.equal(r_squared_result_without_adjustedR, r_squared_builtin, check.attributes = FALSE)
```

```{r}
lm_model= lm(y ~ fitted_values)
built_in_adj_r_squared= summary(lm_model)$adj.r.squared

r_squared_result_with_adjustedR = r_squared(y, fitted_values, p = 1, withadjr = TRUE)$Adjusted_R_Squared

all.equal(r_squared_result_with_adjustedR, built_in_adj_r_squared, check.attributes = FALSE)
```


Now we comparing against the original R functions on simulated dataset to test the efficiency. In the benchmark(), I will not check the correctness, since we already did above.

```{r}
# use Benchmark() for slr() function vs. lm() function
bench::mark(
  result_slr = slr_result$Beta0 + slr_result$Beta1,
  builtin_lm = coef(lm_model)[1] + coef(lm_model)[2],
  check = FALSE
)
```

```{r}
# use Benchmark() for mlr() function vs. lm() function
bench::mark(
  result_mlr = mlr_result$Beta,
  builtin_lm_mlr = coef(lm_mlr_model),
  check = FALSE
)
```

```{r}
# use Benchmark() for ci() function vs. confint() function
bench::mark(
  ci(X, y),
  confint(lm_model),
  check = FALSE
)
```

```{r}
# use Benchmark() for plot_regression() function vs. plot() function
bench::mark(
  plot_regression(x, y),
  plot(x, y),
  check = FALSE
)
```

```{r}
# use Benchmark() for r_squared() function vs. lm() function for without adjusted R_square
bench::mark(
  r_squared(y, fitted_values, p = 1, withadjr = FALSE)$R_Squared,
  summary(lm_model)$r.squared,
  check = FALSE
)
```

```{r}
# use Benchmark() for r_squared() function vs. lm() function for adjusted R_square
bench::mark(
  r_squared(y, fitted_values, p = 1, withadjr = TRUE)$Adjusted_R_Squared,
  summary(lm_model)$adj.r.squared,
  check = FALSE
)

```
